Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-03-10 tex/nusselt_paper.tex
finishes off pre-PDP paper stuff

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved flows. 
The time- and horizontally-averaged profile is removed in all cases.  
(a) At high $\epsilon$, shock systems form near the upper downflow lanes 
($x \approx 45, z \approx 15-19$) at sufficiently high Ra.
Shock-heated fluid then flows into the downflows as the shocks propagate across upflows.
(b) At low $\epsilon$ but at the same Ra, shock systems are absent, 
but otherwise the dynamics are similar.  
(c) As Ra is increased, downflows no longer span
the entirety of the domain and individual 
small eddies are responsible for carrying the flux.
\label{fig:entropy_snapshots} }
\end{figure}

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.
At low to moderate Ra, 
Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
At large Ra, Nu $\propto$ Ra$^{1/5}$ 
at $\epsilon = 0.5$.
The scaling of Nu with Ra 
is unclear at low $\epsilon$ once Ra is sufficiently large
for shearing states to occur.  It would be beneficial to study
low $\epsilon$ flows with fixed-flux boundary conditions or
no-slip boundary conditions that disallow time-dependent shear states.

>>>>

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/snapshots_fig.png}
\caption{Characteristic entropy fluctuations in evolved flows roughly
140$t_b$ after the start of simulations. 
The time- and horizontally-averaged profile is removed in all cases.  
(a) An $\epsilon = 10^{-4}$, low Ma flow. (b) An $\epsilon = 0.5$, flow,
in which shock systems can be seen in the upper atmosphere (e.g.
$(x, z) \approx (30, 18-19), (70, 15-19))$.
(c) A high Ra, $\epsilon = 0.5$ case.  Convective structures become
much smaller scale, and shock systems can be see near $(x, z) \approx (30, 16-19),
(65, 17-19)$.
\label{fig:entropy_snapshots} }
\end{figure}

@@

The variation of Nu with Ra is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.
At low to moderate Ra, 
Nu $\propto$ Ra$^{1/3}$ regardless of $\epsilon$,
reminiscent of scaling laws in classical \RB theory \cite{king&all2012}.
At large Ra, Nu $\propto$ Ra$^{1/5}$ 
at $\epsilon = 0.5$.
The scaling of Nu with Ra 
is unclear at low $\epsilon$ once Ra is sufficiently large
for shearing states to occur.  It is also important to note that
the value of Nu is heavily dependent upon the specific thermodynamic
structures of the solution, as double roll states will transport
heat more efficiently than single roll states, and slight changes in
Ra can result in a solution latching on to one solution or the other.
